Finally Tagless, Partially Evaluated

### 2007-07-27 tagless/tagless-final.tex
Emphasize simplity in contributions

To reiterate, we do \emph{not} propose any new language
feature or new technique. We use features already present in
mainstream functional languages---Hindley-Milner
type system with either an inference\hyp preserving module system or
constructor classes, as realized in ML and Haskell 98---and techniques
which have all appeared in the literature, to
solve the problem that was stated in the published record as
unsolved and likely unsolvable in ML or Haskell 98
without extensions. The simplicity of our solution and its
use of only mainstream features makes it more practical to build typed,
embedded DSLs.
\begin{comment}
We may claim some contribution about type-preserving CPS. Check
related work section in \cite{Guillemette-Monier-PLPV}, especially
check the work of Shao on type-preserving CPS in Flint. The PLPV paper
in related work shows other tasks, including closure conversion, which
we may tackle in our approach. We may be able to write a
type-preserving, assured compiler, whose properties and assured by HM.
\end{comment}

>>>>

To reiterate, we do \emph{not} propose any new language
feature or \ifshort new \else even any new programming \fi technique.
\ifshort
We
\else
Rather, we solve an open problem by a novel combination of simple types
and existing techniques.  More precisely, we
\fi
use features already present in
mainstream functional languages---Hindley-Milner
type system with either an inference\hyp preserving module system or
constructor classes, as realized in ML and Haskell 98---and techniques
which have all appeared in the literature, to
solve a problem that was stated in the published record as
unsolved and likely unsolvable in ML or Haskell 98
without extensions. The simplicity of our solution and its
use of only mainstream features \ifshort\else are virtues that \fi make it more practical to build typed,
embedded DSLs.
\begin{comment}
We may claim some contribution about type-preserving CPS. Check
related work section in \cite{Guillemette-Monier-PLPV}, especially
check the work of Shao on type-preserving CPS in Flint. The PLPV paper
in related work shows other tasks, including closure conversion, which
we may tackle in our approach. We may be able to write a
type-preserving, assured compiler, whose properties and assured by HM.
\end{comment}
